Kolmogorov-Smirnov

### 2020-04-09 ks/ks.Rmd
Use wide table with percentages

```{r}
df_wide <- spread(df, proteome, f)
```

@@

```{r}
knitr::kable(df_wide, caption = "Fraction of epitopes overlapping with transmembrane helix")
```

>>>>

```{r}
df_wide <- spread(df, proteome, f)
df_wide$covid <- formatC(100.0 * df_wide$covid, digits = 3)
df_wide$human <- formatC(100.0 * df_wide$human, digits = 3)
```

@@

```{r}
knitr::kable(df_wide, caption = "Percentage of epitopes overlapping with transmembrane helix")
```
